Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-15 paper.qmd
fixes

## **Abstract**

@@

![](images/Screenshot 2024-12-15 at 2.38.35 AM.png)

```{r}
renamed_data <- completed_data %>%
  rename(
    "Residential Segregation Index" = Residential.Segregation.Index,
    "Median Household Income" = Median.Household.Income,
    "Median Property Tax" = Median.Prop.Tax,
    "School Funding Adequacy" = School.Funding.Adequacy, 
    "Average Life Expectancy" = Life.Expectancy,
    "% Limited Access to Healthy Foods" = X..Limited.Access.to.Healthy.Foods,
    "% Uninsured Adults" = X..Uninsured.Adults,
    "Region" = Region_fac,
    "School Funding Binary" =School.Funding.Cat)

datasummary_skim(
  renamed_data,
  title = "Customized Summary Table")

>>>>

## Abstract

@@

```{r}
renamed_data <- completed_data %>%
  rename(
    "Residential Segregation" = Residential.Segregation.Index,
    "Median Household Income" = Median.Household.Income,
    "Median Property Tax" = Median.Prop.Tax,
    "School Funding Adequacy" = School.Funding.Adequacy, 
    "Life Expectancy" = Life.Expectancy,
    "% Limited Access, Healthy Foods" = X..Limited.Access.to.Healthy.Foods,
    "% Uninsured Adults" = X..Uninsured.Adults,
    "Region" = Region_fac,
    "School Funding Binary" =School.Funding.Cat)

skim_table <- datasummary_skim(
  renamed_data,
  title = "Summary Statistics")
